---
title: "find-packages"
author: "Daniel Fuller"
date: "11/21/2019"
output:
    html_document:
      keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


---
title: "PA Task View"
author: "Daniel Fuller"
date: '2023-06-15'
output:
      html_document:
        keep_md: true
---



## Creating a task view for physical activity researchers

First step is use the `cranly` package to see what is out there. I found this tutorial to help https://rviews.rstudio.com/2018/05/31/exploring-r-packages/. Now I have a tidy dataframe with all the packages. 


```{r}
library(cranly)
package_db <- clean_CRAN_db(tools::CRAN_package_db())
```

## Search dataframe for physical activity related packages

I have used the search terms outlined in the code below. The search attempts to capture packages related to human activity recognition using both research devices and accelerometer or GPS data AND analysis of data form commercial devices (e.g., Fitbit). 

I had originally included the term `exercise` but that search included many packages that were not related to human activity recognition. I also did the same search in title but that did not help and only returned 1 result that was already captured in the description search. 

```{r}
library(stringr)
library(dplyr)
library(kableExtra)
```

```{r}
pa_search <-
    c(
        "physical activity",
        "actigraph",
        "Actigraph",
        "fitbit",
        "garmin",
        "geneactiv",
        "apple health",
        "google fit",
        "samsung health",
        "exercise",
        "omron",
        "actilife",
        "cycling",
        "swimming",
        "activity counts",
        "sedentary",
        "activPAL",
        "accelerometer", 
        "human activity recognition",
        "global positionning sytems",
        "wahoo",
        "whoop",
        "suunto",
        "human activity"
    )

package_db$pa <- str_extract_all(package_db$description, paste(pa_search, collapse = "|"))

pa_packages <- filter(package_db, pa != "character(0)")
```

From this search there are 83 packages are designed to analyse some type of physical activity data.

```{r eval=FALSE, include=FALSE}
table(pa_packages$package)
```

```{r}
pa_pkg_names <- pa_packages$package
```

## Packages' description

```{r}
pa_packages %>% select(package, description) %>%
   kable() %>%
   kable_styling("striped", full_width = FALSE) %>% 
   column_spec(2, width_max = 50)
```

## Manual search of the packages suggests the following packages are important

Core Packages


* GGIR 
* fitbitr
* HMMpa
* MIMSunit
* mMARCH.AC
* walkboutr

Packages


* acc
* accelerometry
* accelmissing
* actilifecounts
* activAnalyzer
* activPAL
* cycleRtools
* fitbitScraper
* fitbitViz
* GENEAclassify
* GENEAread
* GENEAsphere
* GGIRread
* lifelogr
* PASenseWear
* pawacc
* PhysActBedRest
* PhysicalActivity
* read.gt3x
* Sojourn.Data
* SwimmeR
* trackeRapp
* walkboutr
