---
title: "find-packages"
author: "Javad Khataei"
date: "11/21/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


---
title: "PA Task View"
author: "Daniel Fuller"
date: '2018-06-07'
output:
      html_document:
        keep_md: true
---



## Creating a task view for physical activity researchers

First step is use the `cranly` package to see what is out there. I found this tutorial to help https://rviews.rstudio.com/2018/05/31/exploring-r-packages/. Now I have a tidy dataframe with all the packages. 




```{r}
library(cranly)
package_db <- clean_CRAN_db(tools::CRAN_package_db())
```

## Search dataframe for physical activity related packages

I have used the search terms:

- physical activity
- actigraph
- fitbit
- garmin
- geneactiv
- apple health
- google fit
- samsung health

I had originally included the term `exercise` but that search included many packages that were not related to physical activity. I also did the same search in title but that did not help and only returned 1 result that was already captured in the description search. 


```{r}
library(stringr)
library(dplyr)
library(kableExtra)
```

```{r}
pa_search <-
    c(
        "physical activity",
        "actigraph",
        "Actigraph",
        "fitbit",
        "garmin",
        "geneactiv",
        "apple health",
        "google fit",
        "samsung health",
        "exercise",
        "omron",
        "actilife",
        "cycling",
        "swimming",
        "activity counts",
        "sedentary",
        "activPAL"
    )

package_db$pa <-
    str_extract_all(package_db$description, paste(pa_search, collapse = "|"))
pa_packages <- filter(package_db, pa != "character(0)")
```

From this search there are 10 packages are designed to analyse some type of physical activity data.


```{r eval=FALSE, include=FALSE}
table(pa_packages$package)
```


```{r}
pa_pkg_names <- pa_packages$package
```

## Packages' description

```{r}
pa_packages %>% select(package, description) %>%
   kable() %>%
   kable_styling("striped", full_width = F) %>% 
   column_spec(2, width_max = 100)
```




<!-- Just for fun make a network of the packages. -->


<!-- ```{r} -->
<!-- package_network <- build_network(package_db) -->
<!-- pa_packages_network <- package_with(package_network, name = c(pa_pkg_names)) -->
<!-- plot(package_network, package = pa_packages_network, legend = TRUE) -->
<!-- ``` -->
